\textit{Supporting Information for}: Memory for television episodes preserves event content while introducing new across-event similarities

### 2020-01-06 paper/supporting_information.tex
resized figs to avoid covering page numbers
updated title and author info to match updates in main

\title{\textit{Supporting Information for}: How is experience transformed into memory?}
\author{Andrew C. Heusser, Paxton C. Fitzpatrick, and Jeremy R. Manning\\Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\Corresponding author: jeremy.r.manning@dartmouth.edu}

@@

\begin{figure}[p!]
  \centering
  \includegraphics[width=\textwidth]{figs/trajectory_wasserstein}
  \caption{\small \textbf{Trajectories using Wasserstein distance for choosing $K$.}  We replicated the trajectory analysis using Wasserstein distance, a parameter-free procedure for choosing $K$. Overall, the pattern of findings is quite similar to our main approach, but resulted in a smaller number of events.}
  \label{fig:trajectory_wasserstein}
  \end{figure}

>>>>

\title{\textit{Supporting Information for}: Memory for television episodes preserves event content while introducing new across-event similarities}
\author{Andrew C. Heusser\textsuperscript{1, 2}, Paxton C. Fitzpatrick\textsuperscript{1}, and Jeremy R. Manning\textsuperscript{1, *}\\\textsuperscript{1}Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\\textsuperscript{2}Akili Interactive\\Boston, MA 02110\\\textsuperscript{*}Corresponding author: jeremy.r.manning@dartmouth.edu}

@@

\begin{figure}[p!]
\centering
\includegraphics[width=.9\textwidth]{figs/k_optimization}
\caption{\small \textbf{Video and recall trajectory $K$-optimization functions.}  We selected the optimal $K$-value for the video and each recall trajectory, using the formula described in \textit{Methods}. This computation resulted in a curve for each trajectory, describing the regularized ratio of the average within-event topic vector correlation to the average across-event topic vector correlation, as a function of $K$.}
\label{fig:k_optimization}
\end{figure}

\
